Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-16 paper/main.tex
Finalize most optional phrasing suggestions

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize the perception of
spatial information in 14 subjects that were watching an audio-visual Hollywood
movie and listened to the movie's audio-description (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we test if an auditory narrative could
localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
general linear model (GLM) $t$-contrasts that are based on annotations of
selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
that we conducted previously to localize the PPA in the same participants.
% no refs in abstract (probably)
%\citep{sengupata2016extension}.  results: group AV
On a group level, results for a visual movie stimulus show significantly
increased hemodynamic activity spatially overlapping with a traditionally
localized PPA but also extending into earlier visual cortices.
% results: group AD
Results for the audio-description stimulus reveal significant activation
restricted to the anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provide further evidence that the PPA can be divided into functional
subregions.
% localizer substitute
[An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.]
\end{abstract}

@@

\begin{itemize}
    \item text in [brackets] can probably be deleted
    \item imo AD and AV can be written as movie and audio-description
\end{itemize}

@@

% literature review overview 1: imagination & haptic exploration
Increased hemodynamic activity in the PPA generalizes to mental imagination of
landscapes \citep{ocraven2000mental} and haptic exploration of scenes
constructed from LEGO blocks \citep{wolbers2011modality}.
% O'Craven: watching pictures
In a study conducted by \cite{ocraven2000mental} participants viewed alternating
blocks of pictures showing familiar places and famous faces during an initial
experimental paradigm.
% O'Craven: mental imagery
In a subsequent paradigm, participants were instructed to ``form a vivid mental
image'' of the previously viewed pictures.
% O'Craven results
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.
% Wolbers: haptic exploration
In a block design study conducted by \cite{wolbers2011modality} the PPA of
[sighted] participants showed increased activation during a delayed
match-to-sample task of haptically explored scenes constructed from LEGO bricks
compared to abstract geometric objects.
% Wolbers: connectivity analysis

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
All reviewed studies share three common aspects:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-design paradigms to maximize detection power.
Further, they usually employed an explicit (perceptual) judgement task.
% conceptualized stimuli and block: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantage of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of a[n
explicit] perceptual task, experience our rich/multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Third, the reviewed studies averaged results across 7-11 subjects.
% averaging pros and cons
The averaging approach improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

@@

% traditionally
Traditionally, researchers design stimuli that presumably would trigger the
perceptual process of interest while also controlling confounding variables
(e.g. color, luminance).
% our approach: annotation and regressors
Naturalistic stimuli mimic how we experience the world more closely but have the
drawback that they are usually fix and that their temporal structure is unknown.
% annotation ftw
Hence, we annotated the temporal structure of various stimulus features that
later served as basis [for GLM regressors] to model hemodynamic responses.

% AV anno
For the analysis of the AV stimulus, we took advantage of a previously published
annotation of [the 869] movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer within the environment of the movie by either switching to another
setting or switching the perspective within the same setting.
% AV regressors/events
Each cut was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

@@

% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects.
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset (Z>2.3, p<.05 cluster-corrected).
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space (Z>3.4, p<.05 cluster-corrected).
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

% previous studies: no task
Usually studies that use small sets of experimentally controlled stimuli also
employ a task to keep subjects attentive to the stimuli.
% but: Epstein (1998)
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a perceptual judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but still: we are different
Our paradigm still differs from \citep{epstein1998ppa} because the modeled
stimulus features were incidentally embedded in a continuous stream of auditory
information preventing participants from making assumptions about the
investigated perceptual process.
% concluding statement: kinda automatic process
Hence, current results also suggest that verbal spatial information is processed
in the anterior PPA casually and does not [necessarily] rely on [deliberately]
paying attention to verbal spatial information.

@@

% AD annotation > AV annotation
Given that the annotation of nouns offered a more precise way to operationalize
the perception of spatial information than the annotation of cuts and locations,
we also hypothesized that analyzing the data from the audio-description could
localize the PPA in individual persons.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
$t$-threshold in $t$-map from one of three contrasts by visual judgment, we used
the same contrast and threshold (Z>3.4, p<.05 cluster-corrected) for all
subjects.
% in the current study
The audio-description yielded significant bilateral clusters in 9 of 14 subjects
(of which sub-04 shows only a right-lateralized PPA ROI), and a unilateral
significant cluster in one subject.
% similar: anterior part
Similarly to the group average results, results on an individual level also
revealed that clusters are spatially restricted to the anterior part of
individual PPAs.
% conclusion
Thus, the cluster location and size found on the group level is not just a
by-product of the averaging process but a reliable pattern across results of
individual study participants.
% concluding statement
Further, our exploratory analysis suggests that a naturalistic auditory stimulus
can [in principle] be applied to localize (the anterior part) of a higher-level
visual area in the majority of subjects.
% one threshold (and contrast) to rule them all
Nevertheless, further studies that aim for individual diagnostics / ROI
localization should inspect more than one contrast, and use an individual
threshold or a sphere around the local maximum \citep{poldrack2007region} in the
parahippocampal region.

@@

% question
The fact that clusters from the auditory stimulus are spatially restricted to
the anterior part of clusters from the visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual compared to the verbal stimuli.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
Contrary, the aPPA is functionally more responsive than the pPPA to high-level
features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
abstract identity/category \citep{marchette2015outside, watson2016patterns}) and
objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
Contrary, the aPPA is more strongly functionally connected to portions of the
default mode network[, including caudal inferior parietal lobe (cIPL), the
restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
temporal lobe] \citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to a hypothesis by \citep{baldassano2013differential} the PPA consists
of subregions that process different aspects of a visual scene and cooperate to
build a complete scene representation.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.  pPPA
Similarly, our results suggest that the pPPA is more concerned with visual
aspects immanent in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) as immanent in both visual and
verbal stimuli.

@@

\todo[inline]{scientific data has no conclusion -> last paragraph}
% natural stimulation
In summary, natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} offer an easy to implement, continuous,
complex, immersive, task-free paradigm that more closely resembles our natural
dynamic environment than traditional experimental paradigms.
% method
We took advantage of three fMRI datasets and two stimulus annotations that are
part of the studyforrest dataset
\href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
perception of spatial information embedded an audio-visual movie and an auditory
narrative, and compare current results to results gained from a traditional
visual localizer.
% results
In general, results add evidence that a model-driven GLM analysis based on
annotations can be run on data from naturalistic stimuli to localize concise
functional areas and networks correlating with specific perceptual processes.
% interpretation
More specifically, our results demonstrate that increased activation in the PPA
during the perception of static pictures generalizes to the perception of
spatial information embedded in a movie and an exclusively auditory stimulus.
% interpretation: aPPA vs. pPPA
Further, our results provide evidence that the PPA can be divided into
functional subregions that [might] work together during the perception of visual
scenes.
% interpretation
Lastly, a naturally engaging auditory narrative might - in principle -
substitute a visual paradigm to localize the anterior part of the PPA in
subjects who are not [willing or] able to follow task instructions during brain
scanning.

@@

\section*{Figures Legends}

\todo[inline]{Figures \& Tables have their own section??? the editor puts them
where he wants them?}

\emph{We discourage the inclusion of figures in the
Supplementary Information \textendash{} all key figures should be included here
in the main Figure section.}

\emph{Figure legend must total no more
than 350 words, and may contain literature references.}

\section*{Tables}

\emph{tables provide summary information but should not be used to present
primary data (i.e. measurements).}

>>>>

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize the perception of
spatial information in 14 subjects that were watching an audio-visual Hollywood
movie and listened to the movie's audio-description (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we test if an auditory narrative could
localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
general linear model (GLM) $t$-contrasts that are based on annotations of
selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
that we conducted previously to localize the PPA in the same participants.
% no refs in abstract (probably)
%\citep{sengupata2016extension}.  results: group AV
On a group level, results for a visual movie stimulus show significantly
increased hemodynamic activity spatially overlapping with a traditionally
localized PPA but also extending into earlier visual cortices.
% results: group AD
Results for the audio-description stimulus reveal significant activation
restricted to the anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provide further evidence that the PPA can be divided into functional
subregions.
\end{abstract}

@@

\begin{itemize}
    \item imo AD and AV can be written as movie and audio-description
\end{itemize}

@@

% literature review overview 1: imagination & haptic exploration
Increased hemodynamic activity in the PPA generalizes to mental imagination of
landscapes \citep{ocraven2000mental} and haptic exploration of scenes
constructed from LEGO blocks \citep{wolbers2011modality}.
% O'Craven: watching pictures
In a study conducted by \cite{ocraven2000mental} participants viewed alternating
blocks of pictures showing familiar places and famous faces during an initial
experimental paradigm.
% O'Craven: mental imagery
In a subsequent paradigm, participants were instructed to ``form a vivid mental
image'' of the previously viewed pictures.
% O'Craven results
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.
% Wolbers: haptic exploration
In a block design study conducted by \cite{wolbers2011modality} the PPA of
participants showed increased activation during a delayed
match-to-sample task of haptically explored scenes constructed from LEGO bricks
compared to abstract geometric objects.
% Wolbers: connectivity analysis

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
All reviewed studies share three common aspects:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-design paradigms to maximize detection power.
Further, they usually employed an explicit (perceptual) judgement task.
% conceptualized stimuli and block: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantage of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of an
explicit perceptual task, experience our rich/multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Third, the reviewed studies averaged results across 7-11 subjects.
% averaging pros and cons
The averaging approach improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

@@

% traditionally
Traditionally, researchers design stimuli that presumably would trigger the
perceptual process of interest while also controlling confounding variables
(e.g. color, luminance).
% our approach: annotation and regressors
Naturalistic stimuli mimic how we experience the world more closely but have the
drawback that they are usually fix and that their temporal structure is unknown.
% annotation ftw
Hence, we annotated the temporal structure of various stimulus features that
later served as basis for modeling hemodynamic responses.

% AV anno
For the analysis of the AV stimulus, we took advantage of a previously published
annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer within the environment of the movie by either switching to another
setting or switching the perspective within the same setting.
% AV regressors/events
Each cut was put into one of the following five categories (see Table
\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).

@@

% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects.
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset (Z>2.3, p<.05 cluster-corrected).
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space (Z>3.4, p<.05 cluster-corrected).
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts voxels of
significant clusters in almost all subjects.

@@

% previous studies: no task
Usually studies that use small sets of experimentally controlled stimuli also
employ a task to keep subjects attentive to the stimuli.
% but: Epstein (1998)
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a perceptual judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but still: we are different
Our paradigm still differs from \citep{epstein1998ppa} because the modeled
stimulus features were incidentally embedded in a continuous stream of auditory
information preventing participants from making assumptions about the
investigated perceptual process.
% concluding statement: kinda automatic process
Hence, current results also suggest that verbal spatial information is processed
in the anterior PPA casually and does not necessarily rely on deliberately
paying attention to verbal spatial information.

@@

% AD annotation > AV annotation
Given that the annotation of nouns offered a more precise way to operationalize
the perception of spatial information than the annotation of cuts and locations,
we also hypothesized that analyzing the data from the audio-description could
localize the PPA in individual persons.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
$t$-threshold in $t$-map from one of three contrasts by visual judgment, we used
the same contrast and threshold (Z>3.4, p<.05 cluster-corrected) for all
subjects.
% in the current study
The audio-description yielded significant bilateral clusters in 9 of 14 subjects
(of which sub-04 shows only a right-lateralized PPA ROI), and a unilateral
significant cluster in one subject.
% similar: anterior part
Similarly to the group average results, results on an individual level also
revealed that clusters are spatially restricted to the anterior part of
individual PPAs.
% conclusion
Thus, the cluster location and size found on the group level is not just a
by-product of the averaging process but a reliable pattern across results of
individual study participants.
% concluding statement
Further, our exploratory analysis suggests that a naturalistic auditory stimulus
can, in principle, be applied to localize (the anterior part) of a higher-level
visual area in the majority of subjects.
% one threshold (and contrast) to rule them all
Nevertheless, further studies that aim for individual diagnostics / ROI
localization should inspect more than one contrast, and use an individual
threshold or a sphere around the local maximum \citep{poldrack2007region} in the
parahippocampal region.

@@

% question
The fact that clusters from the auditory stimulus are spatially restricted to
the anterior part of clusters from the visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual compared to the verbal stimuli.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
Contrary, the aPPA is functionally more responsive than the pPPA to high-level
features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
abstract identity/category \citep{marchette2015outside, watson2016patterns}) and
objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
Contrary, the aPPA is more strongly functionally connected to portions of the
default mode network, including caudal inferior parietal lobe (cIPL), the
restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
temporal lobe \citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to a hypothesis by \citep{baldassano2013differential} the PPA consists
of subregions that process different aspects of a visual scene and cooperate to
build a complete scene representation.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.  pPPA
Similarly, our results suggest that the pPPA is more concerned with visual
aspects immanent in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) as immanent in both visual and
verbal stimuli.

@@

% natural stimulation
In summary, natural stimuli like movies \citep{eickhoff2020towards,
hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{hamilton2018revolution, honey2012not, lerner2011topographic,
silbert2014coupled, wilson2008beyond} offer an easy to implement, continuous,
complex, immersive, task-free paradigm that more closely resembles our natural
dynamic environment than traditional experimental paradigms.
% method
We took advantage of three fMRI datasets and two stimulus annotations that are
part of the studyforrest dataset
\href{http://www.studyforrest.org}{studyforrest.org} to operationalize the
perception of spatial information embedded an audio-visual movie and an auditory
narrative, and compare current results to results gained from a traditional
visual localizer.
% results
In general, results add evidence that a model-driven GLM analysis based on
annotations can be run on data from naturalistic stimuli to localize concise
functional areas and networks correlating with specific perceptual processes.
% interpretation
More specifically, our results demonstrate that increased activation in the PPA
during the perception of static pictures generalizes to the perception of
spatial information embedded in a movie and an exclusively auditory stimulus.
% interpretation: aPPA vs. pPPA
Further, our results provide evidence that the PPA can be divided into
functional subregions that coactivate during the perception of visual
scenes.
% interpretation
Lastly, a naturally engaging auditory narrative might - in principle -
substitute a visual paradigm to localize the anterior part of the PPA in
individuals with conditions that make them unable to follow task instructions
during brain scanning.

@@
